% This tex document is a resume template for a software engineer
% The author is Ted Chang. You can contact him at
% ted.g.zhang@live.com
% compile command: 
% [ted@ted resume]$ latex CurriculumVitae.tex
% [ted@ted resume]$ dvipdf CurriculumVitae.dvi
\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\textheight=10in
\pagestyle{empty}
%\raggedbottom
\raggedright
%\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }


% DEFINITIONS FOR CV
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1} #2 \end{verse}}
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[3]{{ \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\}}

% Following is contact information (Phone number, email, home page)
\newcommand{\contact}[3]{\vspace*{-8pt} \begin{center}{\LARGE \scshape {#1}}\\ #2 \lineunder
    #3 \end{center} \vspace*{-8pt}
}
% Following is project
\newcommand{\project}[4]{{#1}\\ \textbf{Project Description}:
  {#2}\\ \textbf{Job Description}: {#3}\\ \textbf{Tools}: {#4}\vspace*{3pt}}

% Following is achievement list you have gained
\newenvironment{achievements}{\begin{list}{$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{6pt}\end{list}}

%\newcommand{\schoolwithcourses}[4]{
% \textbf{#1} #2 $\bullet$ #3\\ 
%#4 $\bullet$  Selected Coursework:\\
%\vspace*{5pt}
%}

\newcommand{\school}[2]{\textbf{#1} $\bullet$ #2 \vspace*{5pt}}
% END CV DEFINITIONS


\begin{document}

\small
\smallskip
\vspace*{-44pt}

\contact{Guangkai Zhang}
{Haidian District, Beijing}
{15811559385 $\bullet$ ted.g.zhang@live.com $\bullet$ https://github.com/Ted-Chang}


% Education information goes here
\header{Education}
\school{Xi'an Univesity of Architecture and
  Technology}{Bachelor of Computer Information Management. 2008}
% Education information ends


% Work Experience goes here
\header{Work Experience}
% LeCloud work experience goes here
\employer{Le Cloud}{2016.6-present}{Senior Software Engineer}
\begin{achievements}
\item Help develop and maintain the cloud storage system of LeCloud, mainly focused on Ceph development and storage performance tuning.
\end{achievements}

% EMC Corp. work experience goes here
\employer{EMC Corp.}{2012.6-2016.6}{Senior Software Engineer}
\begin{achievements}
\item
  \project{EMC VNX Rockies Release}
          {Help deliver EMC Mid-Range storage product VNX. Mainly focused on storage virtualization subsystem MLU(Mapped LUN) which is similar to Linux Device Mapper. Features and functions including Advanced Snapshot, Auto Tiering, ODX(Offload Data Xfer), Storage Pool Space Reclaim, etc.}
          {Investigate bugs found during system quality tests. Participate in discussion of feature development. Write HLD and functional spec.}
          {Distributed Lock Service, SCSI protocol, File System, Transaction Management, GCC, GDB, various storage test tools}

\item
  \project{EMC Unity KittyHawk/Falcon Release}
          {Help deliver EMC Entry level storage product Unity. Features include IMLR(In Memory Log Replay), PFDC(Persistent File Data Cache), etc.}
          {Participate in discussion of feature development. Write automated functional test cases and unit test cases. Investigate bugs found during system quality tests.}
          {File System Log, File System Transaction Management, GCC, GDB}
\end{achievements}

% Tencent work experience goes here
\employer{Tencent Technology - Beijing Branch}{2011.7-2012.3} {Software Engineer}
\begin{achievements}
\item Develop the QQ Account Protect module which protect users from web phishing.
\item Analyze scanning log of the VDC(Virus Data Center) with python.
\item Develop the QQ AntiVirus policy dispatch module.
\end{achievements}

% BWSTOR work experience goes here
\employer{BWSTOR - Beijing Branch}{2008.7-2011.7}{Software Engineer}
\begin{achievements}
\item 
  \project{BWFS SAN Windows Client performance tuning.}
          {Assist the team leader to improve the I/O Performance of BWFS SAN Windows Client 5.0.}
          {Investigate performance analyzing tools, benchmark testing tools. Do performance test and performance data analyzing.}
          {iometer, iozone.}

\item 
  \project{Port BWFS SAN Windows Client and VDisk to 64bit Windows.}
          {Porting the BWFS SAN Windows Client file system driver and VDisk driver to 64bit Windows. The VDisk driver is a SCSI Miniport driver which provide functions as iSCSI initiator but using the NBD(Network Block Device) protocol.}
          {Port drivers, fix bugs and do white box test.}
          {WinDDK, WinDbg.}

\item 
  \project{Snapshot component for the BWFS SAN Windows Client.}
          {The snapshot component of BWFS SAN Windows Client contains two parts: a user mode component work with FalconStor's snapshot daemon and a driver component provides functions such as flushing, freezing and thawing the virtual disk device created by client's file system driver.}
          {Develop the user mode component, do code review, fix bugs and do white box test.}
          {Platform SDK}

\item 
  \project{SCSI I/O feature for the BWFS SAN Windows Client.}
          {Break the 4G maximum addressable LBA restriction in Windows XP so customers can export a single device which is larger than 2TB(block size 512 Bytes) to the Windows XP client.}
          {Develop the user mode and kernel mode components, fix bugs and do white box test.}
          {Platform SDK, WinDDK, WinDbg.}

\item 
  \project{File system level flow control feature for the BWFS SAN Windows Client.}
          {Provide the file system level flow control feature so our customers can make use of the network bandwidth reasonably when using iSCSI as the lower device.}
          {Design, develop the user mode and kernel mode components, do code review, fix bugs and do white box test.}
          {Platform SDK, WinDDK, WinDbg, iometer.}

\item 
  \project{ACL feature for the BWFS SAN Windows Client.}
          {Provide Windows ACL feature so our customers can do flexible permission management in the Windows way. We also make this feature compatible with Samba's NT ACL so the ACL can be modified via a Linux Samba export.}
          {Investigate, design, develop the user/kernel mode components and do white box test.}
          {WinDDK, WinDbg, GDB, Samba source.}

\item 
  \project{Multipath component for the BWFS SAN Windows Client.}
          {Provide multipath high availability feature on file system level.}
          {Investigate the mechanism of Linux device mapper, develop sub component of the kernel mode pseudo device layer, do code review and do white box test.}
          {Platform SDK, WinDDK, WinDbg, Linux device mapper source.}

\end{achievements}

\employer{BWSTOR - Beijing Branch}{2008.3-2008.5}{Internship Software Engineer}
\begin{achievements}
\item Develop the BWFS SAN Server Management System 5.0 with shell and perl
\item Apply LTP(Linux Test Project) to BWFS SAN test system.
\end{achievements}
% Work Experience ends


% Skills goes here
\header{Skills}
\begin{achievements}
\item Proficiency in software development in ASM, C, C++, Python.
\item Excellent debugging skills with WinDbg.
\item Familiarity with Windows NT kernel, Windows Driver Model,
  Windows File System Driver development, Windows Storage Stack.
\item Knowledge in SCSI Miniport Driver and Disk Filter Driver.
\item Experience in diagnosing performance problem with Windows
  Performance Toolkit.
\item Technical support experience for foreign customers.
\item Familiarity with GNU/Linux system management.
\end{achievements}
% Skills ends


% Honors and Awards goes here
\header{Honors and Awards}
\begin{achievements}
\item Awarded the 2009 Excellent Project Award from BWSTOR.
\item WDK Community BUG BASH 2010 Prize from osronline.
\end{achievements}
% Honors and Awards ends


\end{document}
